Addition and removal energies of circular quantum dots

### 2017-08-29 Manuscript/paper.tex
Shortened description of CC algo and left/right eigen

The unknown cluster amplitudes in CCSD, $t_{a i}$ and $t_{a b i j}$, are calculated by left-multiplying Eq.\ \eqref{eq:cc_schrodeq} by $\bra{\Phi} \normord{\hat a_i^\dagger \hat a_a} \E^{-\hat{T}}$ and $\bra{\Phi} \normord{\hat a_i^\dagger \hat a_j^\dagger \hat a_b \hat a_a} \E^{-\hat{T}}$, respectively,
\begin{align} \label{eq:ccsd1}
  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_a} \bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0, \\
  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_j^\dagger \hat a_b \hat a_a}\bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0. \notag
\end{align}
After the Fock matrix has been diagonalized, the diagonal components of Eq.\ \eqref{eq:ccsd1} can be separated and, after expanding the exponent in Eq.\ \eqref{eq:cc_heff1}, the non-vanishing terms of the CCSD amplitude equations become,
\begin{gather} \label{eq:ccsd2}
  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_a} \hat{H}_2 \bigl\{\hat{T}_1 + \hat{T}_2 + \hat{T}_1\hat{T}_2 + \frac{1}{2!} \hat{T}_1^{2} + \frac{1}{3!} \hat{T}_1^{3}\}_{\mathrm{c}} \ket{\Phi} = \Delta_{i a} t_{a i} \\
  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_j^\dagger \hat a_b \hat a_a} \hat{H}_2 \bigl\{1 + \hat{T}_1 + \hat{T}_2 + \frac{1}{2} \hat{T}_1^{2} + \hat{T}_1\hat{T}_2 + \frac{1}{2!} \hat{T}_2^{2} + \frac{1}{3!} \hat{T}_1^{3} + \frac{1}{2!} \hat{T}_1^{2} \hat{T}_2 + \frac{1}{4!} \hat{T}_1^{4}\bigr\}_{\mathrm{c}} \ket{\Phi} \notag \\
= \Delta_{i j a b} t_{a b i j} \notag
\end{gather}
where $\Delta$ are the M\o ller--Plesset denominators from Eq.\ \eqref{eq:moellerplessetdenominator}.  As usual, these non-linear equations are solved using an iterative procedure.  One begins with an initial guess for the cluster amplitudes, which are used to calculate the left-hand side of Eq.\ \eqref{eq:ccsd2}.  Dividing by the denominator on the right-hand side gives updated amplitudes which are used to re-evaluate the left-hand side. This process is repeated until the amplitudes reach a fixed point.  Like the HF iterative procedure, employing convergence acceleration techniques can reduce the number of CC iterations required.

@@

In this paper, because the interaction is real and thus the effective Hamiltonian is real, the left- and right-eigenvalues are equivalent. In addition, while the the left- and right-eigenvectors are generally not equal, the differences in their single-particle Eq.\ \eqref{eq:partial_norms_p} or single-hole Eq.\ \eqref{eq:partial_norms_h} natures are, in practice, not significant.  Therefore, only the right-eigenvectors are used in this paper.

>>>>

The unknown cluster amplitudes in CCSD, $t_{a i}$ and $t_{a b i j}$, are calculated by left-multiplying Eq.\ \eqref{eq:cc_schrodeq} by $\bra{\Phi} \normord{\hat a_i^\dagger \hat a_a} \E^{-\hat{T}}$ and $\bra{\Phi} \normord{\hat a_i^\dagger \hat a_j^\dagger \hat a_b \hat a_a} \E^{-\hat{T}}$, respectively,
\begin{align} \label{eq:ccsd1}
  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_a} \bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0, \\
  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_j^\dagger \hat a_b \hat a_a}\bar{H}_{\mathrm{CC}} \ket{\Phi} &= 0. \notag
\end{align}
After the Fock matrix has been diagonalized, the diagonal components of Eq.\ \eqref{eq:ccsd1} can be separated and, after expanding the exponent in Eq.\ \eqref{eq:cc_heff1}, the non-vanishing terms of the CCSD amplitude equations become,
\begin{gather} \label{eq:ccsd2}
  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_a} \hat{H}_2 \bigl\{\hat{T}_1 + \hat{T}_2 + \hat{T}_1\hat{T}_2 + \frac{1}{2!} \hat{T}_1^{2} + \frac{1}{3!} \hat{T}_1^{3}\}_{\mathrm{c}} \ket{\Phi} = \Delta_{i a} t_{a i} \\
  \bra{\Phi} \normord{\hat a_i^\dagger \hat a_j^\dagger \hat a_b \hat a_a} \hat{H}_2 \bigl\{1 + \hat{T}_1 + \hat{T}_2 + \frac{1}{2} \hat{T}_1^{2} + \hat{T}_1\hat{T}_2 + \frac{1}{2!} \hat{T}_2^{2} + \frac{1}{3!} \hat{T}_1^{3} + \frac{1}{2!} \hat{T}_1^{2} \hat{T}_2 + \frac{1}{4!} \hat{T}_1^{4}\bigr\}_{\mathrm{c}} \ket{\Phi} \notag \\
= \Delta_{i j a b} t_{a b i j} \notag
\end{gather}
where $\Delta$ are the M\o ller--Plesset denominators from Eq.\ \eqref{eq:moellerplessetdenominator}.  As usual, these non-linear equations are solved using an iterative procedure where the cluster amplitudes on the right-hand side of Eq.\ \eqref{eq:ccsd2} are updated by calculating the terms on the left-hand side until a fixed point is reached.  Like the HF iterative procedure, employing convergence acceleration techniques can reduce the number of CC iterations required.

@@

In this paper, because the effective Hamiltonian is real, the corresponding left- and right-eigenvalues are equal. In addition, while the the left- and right-eigenvectors are generally not equivalent, the differences in their single-particle Eq.\ \eqref{eq:partial_norms_p} or single-hole Eq.\ \eqref{eq:partial_norms_h} natures are, in practice, not significant.  Therefore, only the right-eigenvectors are used in this paper.
